---
title: "Influence of pandamic to marriage "
subtitle: "The increase of divorce during 2018 - 2023"
author: 
  - Yanfei Huang
thanks: "Code and data are available at: https://open.toronto.ca/dataset/marriage-licence-statistics/."
date: September 19 2024
date-format: long
abstract: "This is about marriage in Toronto from 2018 to present."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
install.packages("tinytex")

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```

# Introduction

This article is about marriage. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of marriage during COVID (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: fig-marriage
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

\newpage

# References
